\section{Results}
The patterns from the free edge Chladni setup for the square plate are shown bellow and labeled with their corresponding frequencies.

The patterns for the clamped edge Chladni setup are not shown because the apparatus failed to visualise them. When the edges are clamped. The tension in the plate is too high to make any significant vibrations. The wave generator used cannot create waves with enough amplitude to create any notable waves. Furthermore, the frequencies required to create the waves are also increased. At high frequencies, the wave generator cannot create vibrations with precise enough frequencies. This is why the Chladni Setup failed to visualise clamped edge situations in this investigation.

\subsection{Wave Equations}
The analytical and the numerical solutions of the wave equation is shown bellow.

The patterns of the analytical and numerical solutions matches each other perfectly at every modes. However, when compared to the actual Chladni waves, there are still some notable differences.

These differences comes from multiple factors and is due to the simplicity of this model. It haven't taken the material properties of the metal plate into account and models waves under free oscillation when they are actually driven by an external source.

The frequencies predicted by this model are all arbitrary and should not be compared to the actual frequencies in the experiment. This is because this model assumes that the waves exists on a non-elastic membrane with negligible thickness. The wave speed therefore is not taken into account. 

\subsection{Forced Wave Equation}